Adaptable Scheduling Policy for Elastic Stream Processing System

### 2019-11-25 paper.tex
Add files via upload

In order to deal with the emerged challenges and satisfy the needs of related markets, varieties of stream data processing platforms targeted in scalability, fault tolerance and computing speed have been developed and deployed, such as Drizzle~\cite{Venkataraman:2017:DFA:3132747.3132750},  Twitter’s Heron~\cite{Kulkarni:2015:THS:2723372.2742788}, LinkedIn’s Samza~\cite{Noghabi:2017:SSS:3137765.3137770}, Apache Kafka~\cite{kreps2011kafka} and Apache Flink~\cite{Carbone2015ApacheFS}. However, these applications are not able to adapt because they lack control over the rate of occurrence of activities. For example, the flow of data at low activity periods can be dramatically different from the flow of data observed at peak periods. One of the most outstanding accomplishments to design an adaptable stream processing application is Dhalion~\cite{Agrawal:2018:DAA:3229863.3275594}~\cite{Floratou:2017:DSS:3137765.3137786}. Dhalion is a library that sits on top of Twitter Heron. It periodically retrieves metrics from Heron's Metrics Managers, detecting any problematic behaviors in these metrics, and take actions to recover the streaming system. Dhalion also supports user-specified policies for more flexibility.

@@

% https://www.youtube.com/watch?v=Dm98w7gkKIA
% \subsection{Drizzle} 
% Drizzle is a low latency execution engine for Apache Spark. It improved Spark Streaming with group scheduling and pre-scheduling to reduce processing latency to the order of 100 ms while maintaining low recovery latency.

@@

{
\bibliographystyle{abbrv}
\bibliography{ref}
}
\end{document}

>>>>

In order to deal with the emerged challenges and satisfy the needs of related markets, varieties of stream data processing platforms targeted in scalability, fault tolerance and computing speed have been developed and deployed, such as Twitter’s Heron~\cite{Kulkarni:2015:THS:2723372.2742788}, LinkedIn’s Samza~\cite{Noghabi:2017:SSS:3137765.3137770}, Apache Kafka~\cite{kreps2011kafka} and Apache Flink~\cite{Carbone2015ApacheFS}. However, these applications are not able to adapt because they lack control over the rate of occurrence of activities. For example, the flow of data at low activity periods can be dramatically different from the flow of data observed at peak periods. One of the most outstanding accomplishments to design an adaptable stream processing application is Dhalion~\cite{Agrawal:2018:DAA:3229863.3275594}~\cite{Floratou:2017:DSS:3137765.3137786}. Dhalion is a library that sits on top of Twitter Heron. It periodically retrieves metrics from Heron's Metrics Managers, detecting any problematic behaviors in these metrics, and take actions to recover the streaming system. Dhalion also supports user-specified policies for more flexibility.

@@

% https://www.youtube.com/watch?v=Dm98w7gkKIA
% \subsection{Drizzle} 
% Drizzle~\cite{Venkataraman:2017:DFA:3132747.3132750},
% Drizzle is a low latency execution engine for Apache Spark. It improved Spark Streaming with group scheduling and pre-scheduling to reduce processing latency to the order of 100 ms while maintaining low recovery latency.

@@

{
% \bibliographystyle{abbrv}
\bibliographystyle{ieeetr}
\bibliography{ref}
}
\end{document}
